The controlled choice design and private paternalism in pawnshop borrowing - STATA documentation

### 2025-04-25 Restud submission/donde_restud-REAL-THING.tex
First set of edits after R&R

\documentclass[12pt, a4paper]{article}

\input{preamble.tex}
%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
\usepackage{xr}
\makeatletter
\newcommand*{\addFileDependency}[1]{
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

@@

\newgeometry{margin=1in}
\linespread{1.25}
\begin{document}

\title{Structured Payment in Pawnshop Borrowing\thanks{We want to thank Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, Anett John, David Laibson, Aprajit Mahajan, Matt Rabin, Mauricio Romero, Charlie Sprenger, Chris Udry, and seminar participants at ITAM, USC, MSU, UC Davis,  UCSD, and USC who provided valuable feedback. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.  Research assistance was financed through faculty grants at ITAM. Our research partner had no say in the design or results of the experiment.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
\date{This draft:  \today \\[2 cm]}

@@

\begin{abstract}
We explore paternalism in the understudied context of high-default pawn lending. We use a novel one-stage, three-armed RCT, including forced and voluntary treatment arms, to point-identify the effects of structured repayment contracts on both the treated and the untreated simultaneously. We find that forcing borrowers into commitment-style contracts decreases the financial cost of pawn loans by 22\% and increases the likelihood of recovering their pawn by 15\%. However, only 11\% of borrowers choose such contracts. We find that borrowers who would not choose regular payments would benefit substantially from getting such contracts, as much as those freely choosing them (no selection on gains).  A paternalistic policy of universal forced commitment archives similar benefits to personalized targeting. 
\end{abstract}

\vspace{.8in}
\noindent \textbf{Keywords: } Paternalism, choice, treatment on the untreated, payment frequency, overconfidence. \textbf{JEL codes:} G41, C93, O16, G21

@@

Pawnshop lending, where borrowers provide gold and other easily sold items to receive overcolleralized loans, are one of the most prevalent forms of credit in the world. loans are one of the oldest and most common forms of borrowing \citep{carter2012pawnshops}. 
In Mexico the scale of pawn lending rivals that of microfinance: during the past three years a single large lender in the country made over 4 million loans to more than a million clients. Compare this to a total of 2.3 million microfinance clients in all of Mexico during 2009 \citep{Pedroza:2010}. Pawn borrowers are not only numerous, they are also economically vulnerable. The vast majority of pawn loans are made to people with relatively low levels of education in times of significant stress.\footnote{A large literature shows stress impairs cognitive function, e.g. \cite{StressReview}.} Despite its prevalence and at-risk clientele, however, pawn lending has received little attention in the literature compared to other financial services.

Financial institutions often use built-in commitment mechanisms like fixed repayment streams to lower default rates and increase their own profits. At the same time, they frequently ``shroud'' these attributes by embedding them as non-negotiable features of the loan contract, presumably because borrowers undervalue commitment and would not demand it, given the choice. \cite{Laibson2018} refers to this practice as ``private paternalism''. When the incentives of firm and client align, as they do in \cite{Laibson2018}, private paternalism can benefit both parties. Pawn lending, however, turns this idea on its head: since the value of the collateral--the pawn--exceeds that of the loan, lenders stand to gain the most when borrowers default.\footnote{An industry standard contract in Mexico City lends 70\% of the value of gold collateral at an interest rate of 7\% for three months. Because gold is highly liquid, the profit from a borrower who defaults is 30\% of the collateral value compared to 15.8\% in interest if a loan is paid in full on the last day.}
Consistent with this idea, and in stark contrast to microfinance, pawn lenders in Mexico City neither send payment reminders to borrowers nor provide commitment features in their contracts. Default is common.\footnote{The default rate in the \emph{status quo} arm of our Mexico City experiment is 44\%.}

This paper presents results from a randomized experiment that answers three key questions. First, does the absence of commitment-style contracts cause default in pawn lending? If so, to what extent does this benefit lenders? Second, if a commitment contract were available would pawn borrowers choose it? Even more importantly, would the \emph{right} borrowers choose it, i.e.\ those who would benefit the most? Third, is there a case for \emph{paternalism}, namely for mandating commitment in pawn lending? If so, should commitment be mandated for all borrowers or can it be effectively targeted? The question of choice versus paternalism is particularly salient in a setting with vulnerable borrowers. Yet comparing voluntary versus paternalistic policies is challenging. Even if commitment lowers financial costs on average, it may be ineffective or even harmful for borrowers who \emph{would not choose} to commit. To meet this challenge we introduce a novel three-armed design, the ``forcing-choice'' design, that allows us to shed light on these three questions in the important and under-studied context of pawn lending.

Our experiment covers just under 5,000 pawnshop clients across six of our partner lender's Mexico City branches. The control arm illustrates the costs of the \emph{status quo} contract: fully 44\% of control borrowers default, losing their pawn along with any payments made towards principal. Worse still, 29\% of those who default do so after making at least one payment towards recovery, a payment that they forfeit upon default. The ``forced commitment'' arm requires borrowers to make three monthly payments, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent.  Finally, the ``commitment choice'' arm offers borrowers the chance to opt in to the same structured monthly contract that is mandated for borrowers in the forced commitment arm.\footnote{When describing this new contract below, we use the terms ``commitment'' and ``structured payment'' interchangeably.}

Because there is no selection into or out of the control (status quo) and forced commitment arms in our experiment, the forcing-choice design can be viewed as a \emph{juxtaposition} of three more familiar experimental designs.\footnote{See section \ref{sec:integrity} for a discussion of how we can be sure that there was no selection into or out of the treatment and forced commitment arms.} The first is a standard two-armed RCT with perfect compliance that point identifies the average treatment effect (ATE) of commitment. The other two are a pair of randomized encouragement designs, each with one-sided non-compliance: one point identifies the effect of commitment for borrowers who would \emph{voluntarily} choose commitment (treatment on the treated: TOT), while the other point identifies the effect of commitment for borrowers who would \emph{not} (treatment on the untreated: TUT). 
Fully evaluating the case for paternalism versus borrower choice requires policymakers to learn not only whether those who demand commitment benefit from it (TOT), but also whether those who \emph{do not} are better off without it (TUT).

Our ATE results show that commitment is strongly effective in lowering financial costs and preventing default in pawnshop lending: the average borrower in the forced arm pays financing costs inclusive of fees that are 22\% lower than the control, and faces a probability of default that is 6.6 percentage points lower (15\% of the mean). In terms of Annual Percentage Rates (APR), the financial cost of borrowing falls by 11 percentage points per loan (19\% of the mean). In short, structured commitment saves borrowers money by charging them fees. The mechanism by which our monthly payment contract achieves these cost savings is intriguing: not only does it speed up payments, it also generates an early \emph{bifurcation} of borrowers into those that will recover their pawns and those that will not. The former are induced to pay faster, saving on interest; the latter pay less towards loans that ultimately default, hence losing less money when they do. While we find that borrowers who experience structured payment contracts are 6 percentage points more likely borrow again from the same lender, a back-of-the-envelope calculation suggests that the commitment contract nevertheless lowers lender profits by \hl{11\% per borrower}. It is thus unsurprising that commitment contracts were unavailable in Mexico city pawnshops outside of our experiment: lenders profit from default.\footnote{Unlike most pawn lenders, our partner operates as a non-profit, donating all of their earnings to philanthropic causes. They approached us and requested help evaluating the causal effect of commitment.}

Given the limited measures that are available to us, we refrain from making definitive welfare statements in this paper, focusing instead on the cost of loan servicing, an important outcome in credit markets.\footnote{\hl{Enrique will find citations for a defensive footnote that goes here, pointing out that lots of papers use this as an outcome measure.}} Nevertheless, we explore the sensitivity of our findings to broader notions of cost. For example, our results are qualitatively robust to deducting transport costs of visiting the branch to make interim payments along with a day of lost wages for each visit. They are also robust to using borrowers' \emph{subjective} values of their pawns rather than the appraised value and to adjusting for lost liquidity from requiring monthly payments.

Despite the large financial cost savings of structured repayment, only 11\% of borrowers in the choice arm opt into the commitment contract. 
Could it be that borrowers who do not choose commitment are those who simply don't need it? 
To answer this question, we carry out a detailed analysis of treatment effect heterogeneity.
We begin by bounding the distribution of individual treatment effects using the marginal outcome distributions from the forced commitment and control arms, following \cite{fan2010sharp}. This approach imposes no assumptions beyond the experimental randomization. We find that \emph{at least} 23\% of borrowers benefit from the structured payment contract. This implies that there must be many borrowers in the choice arm who did not demand this feature despite their \emph{individual treatment effect} from (forced) commitment being positive.

Next, we impose a pair of exclusion restrictions positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it. In other words, we assume that choosing a contract results in the same potential outcome as being assigned that contract. This is a relatively common if often implicit assumption in causal inference.\footnote{Papers that use variation in compulsory schooling laws to identify the returns to schooling, for example, typically interpret their results as the causal effect of additional \emph{education} rather than additional \emph{forced education}. \cite{chamberlain2011bayesian} uses a closely related assumption to develop a theory of optimal treatment choice.} 
It also has testable implications that we fail to reject in our empirical context.\footnote{See\autoref{sec:testing_exclusion} \hl{for details--Frank will move some of this into the body of the text.}}
Under these restrictions, the forcing-choice design point-identifies the TOT and TUT, described above, along with the average selection on gains $\text{ASG} = \text{TOT} - \text{TUT}$, a measure of the empirical relevance of Roy-type selection.
Our estimated TUT effect on financial cost savings is large: \$192 pesos, equivalent to a 10.6 percentage point savings in APR. On average, the borrowers who would \emph{not} choose commitment, would have faced substantially lower financial costs if they had. 
Finally, we combine our experimental treatment and outcome data with survey responses collected for a subset of borrowers to estimate conditional average treatment effects, both TUTs and ATEs, using the Causal Random Forest algorithm of \cite{atheygrf}. We estimate positive conditional average TUT effects for 93\% of the borrowers who did \textit{not} choose the commitment contract. In short, it is extremely difficult to find identifiable groups of borrowers who incur higher financial costs under a commitment contract, even when restricting attention to those who would not choose it voluntarily.

So why do borrowers seem to be leaving money on the table? 
While a simple measure of time inconsistency does not explain the large and positive TUT effect, we find that borrowers systematically overestimate the probability that they will recover their pawn: the average subjective probability of recovery is 92\% compared to a realized probability of 44\%.
Indeed, among borrowers who choose not to commit, we estimate the largest gains from commitment for those who overestimate their probability of recovery \emph{the most}.
This suggests that overconfidence may reduce the demand for commitment.

According to our conditional TUT results discussed above, mandating commitment contracts for all borrowers runs the risk of increasing financial costs for 7\% of the untreated. This raises the question of whether it is possible to assign commitment contracts in a \emph{targeted} way to only those borrowers who are likely to benefit from them. To answer this question, we revisit the causal forest results described above for the subset of borrowers who completed our baseline survey. Importantly, some variables from our survey that predict treatment effect heterogeneity cannot be used for targeting in practice. For example, while overconfident borrowers are more likely to default, targeting based on subjective probability of recovery may incentivize borrowers to change their reports, causing the predictive relationship to break down. Accordingly, our exercise restricts attention to survey variables that would be hard to manipulate (``narrow'' targeting). With this restriction, all of the targeting rules that we explore have relatively weak predictive power. Our best-performing targeting rule only lower the overall mis-targeting rate from 9.7\%--the baseline when all borrowers are assigned to commitment--to 9.5\%.

Our paper makes a number of contributions to the literature. First, we provide a detailed picture of pawn lending, a widespread and important financial service that, despite its prevalence and impact on economically vulnerable borrowers, has received little scholarly attention. While an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}, the behavioral implications of such contracts remain largely unexplored. To our knowledge, ours is the first behavioral paper to focus on pawn lending specifically.

Second, we contribute to the relatively small literature on paternalism and selection-on-gains. In contrast to \cite{Laibson2018}, who studies private paternalism from a theoretical perspective, we show empirically that pawn borrowers would benefit, and lenders would suffer, from a paternalistic policy that mandates commitment in the form of structured repayment contracts. Unlike \cite{Sprenger}, who shows that individuals with the most time-inconsistent preferences are the least likely to demand commitment, we directly identify the treatment effect on the untreated (TUT). This obviates the need to first elicit preferences before testing for negative selection. Furthermore, whereas \cite{Walters} combines a distance-based instrument with structural modeling assumptions to show that students who select into more effective schools have smaller treatment effects ($\text{TOT} < \text{TUT}$), we identify the TUT and TOT effects without the need for a structural model. Instead, we rely on relatively weak exclusion restrictions whose testable implications we fail to reject.

Third, our paper makes a methodological contribution by introducing the ``forcing-choice'' design, a novel three-armed experiment that point identifies treatment effects for choosers (TOT) and non-choosers (TUT) under minimal assumptions.\footnote{A companion STATA package provides simple, regression-based estimators for each of the causal parameters that are identified under this design, along with appropriate cluster-robust standard errors. See \autoref{sec:estimation_inference} for more details.}  
To our knowledge, this is the first paper to simultaneously point identify both quantities in the same experiment without the need for a structural model.\footnote{The forcing-choice design also point identifies the average selection-on-gains $\text{ASG} = \text{TOT} - \text{TUT}$, the average selection bias (ASB)--the difference in untreated potential outcomes for choosers versus non-choosers--and the average selection on levels (ASL)--the analogous comparison for treated potential outcomes. See Section \ref{sec:randchoice}.}
Our approach provides a valuable alternative to existing approaches for studying the relationship between treatment effects and treatment take-up. While the Marginal Treatment Effect (MTE) approach can be applied to either experimental or observational data provided that an instrumental variable is available, applying it requires additional modeling assumptions unless the instrument has a rich support set \citep{mogstad2018using}. The Becker-Degroot-Marschak (BDM) mechanism provides a theoretically attractive alternative that does not depend on structural modeling assumptions, but some recent studies have raised concerns about its reliability in practice \citep{bohm1997eliciting,banerji2014detection,mamadehussene2023reliability}.

The forcing-choice design differs from and complements other multi-armed designs from the literature.
As far as we are aware, our approach is the first to simultaneously identify both the TOT and TUT effects for within the same experiment, allowing us to study the empirical relevance of selection-on-gains.
The TUT effect, in particular, is crucial for considering the case for paternalism.
While \cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they instead identify \emph{two} TOT effects for different groups of ``treated'' households.
The well-known \cite{KarlanZinman2009} design, which randomly assigns interest rates in two stages to separate adverse selection from moral hazard, does not identify a TUT effect.
Like \cite{KarlanZinman2009}, \cite{Beaman2023} employ a two-stage randomization compared to the one-stage, three-armed approach in the forcing-choice design.
And while they identify a number of interesting causal parameters that shed light on the relationship between take-up and treatment effect heterogeneity, \cite{Beaman2023} do not identify a TUT effect or the average selection-on-gains.\footnote{In particular: the identify the ATE of cash grants, the TOT of loans, and the average effect of cash grants for those who would and would not accept a loan. While interesting, these last two effects are not TOT and TUT effects, because effects and compliance are defined with respect ti \emph{different} treatments: grants versus loans.}

>>>>

\documentclass[12pt, a4paper, colorinlistoftodos]{article}

\input{preamble.tex}

%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
\usepackage{authblk}
\makeatletter
\renewcommand\AB@affilsepx{, }
\makeatother
\renewcommand\Authands{ and }
\renewcommand\Affilfont{\small}
\setlength{\affilsep}{0em}
\usepackage{xr}
\makeatletter
\newcommand*{\addFileDependency}[1]{
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

@@

\newgeometry{margin=1in}
\linespread{1.25}

% To-do commands (must go after authblk to avoid clash)
\usepackage{todonotes}
\usepackage{marginnote}
\renewcommand*{\marginfont}{\color{red}\sffamily\scriptsize}
\setlength{\marginparwidth}{2cm}  % prevent todo cutoff
\newcounter{todoListItems}
\newcommand{\todoLink}[2][ ]{
  \addtocounter{todoListItems}{1}
  \todo[caption={\protect\hypertarget{todo\thetodoListItems}{}Translation},size=\tiny,#1]{
    \tiny #2 \hfill \hyperlink{todo\thetodoListItems}{$\uparrow$}
  }
}
\newcommand{\forES}[1]{\todoLink[color=green!20,inline,caption={\thetodoListItems: For @Enrique}]{\textbf{@Enrique} -- #1}}
\newcommand{\forIM}[1]{\todoLink[color=blue!20,inline,caption={\thetodoListItems: For @Isaac}]{\textbf{@Isaac} -- #1}}
\newcommand{\forFdT}[1]{\todoLink[color=red!20,inline,caption={\thetodoListItems: For @Francis}]{\textbf{@Francis} -- #1}}
\newcommand{\forCM}[1]{\todoLink[color=violet!20,inline,caption={\thetodoListItems: For @Craig}]{\textbf{@Craig} -- #1}}
\newcommand{\forAll}[1]{\todoLink[color=orange!20,inline,caption={\thetodoListItems: For All}]{\textbf{@All} -- #1}}

\begin{document}

\listoftodos

\title{Structured Payment in Pawnshop Borrowing: Mandates vs.\ Choice\thanks{We thank Jose Maria Barrero, Camilo García-Jimeno, Andrei Gomberg, Emilio Gutierrez, Anett John, David Laibson, Aprajit Mahajan, Matt Rabin, Mauricio Romero, Charlie Sprenger, Séverine Toussaert, Chris Udry, Jonathan Zinman, and seminar participants at Dartmouth, ITAM, MSU, USC, UC Davis, UCSD, and USC who provided valuable feedback. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.  Research assistance was financed through faculty grants at ITAM. Our research partner had no say in the design or results of the experiment.}}
\author[1]{Francis J.\ DiTraglia}
\author[2]{Craig McIntosh}
\author[3]{Isaac Meza}
\author[4]{Joyce Sadka}
\author[5]{Enrique Seira\thanks{Corresponding Author: \href{mailto:enrique.seira@gmail.com}{enrique.seira@gmail.com}}}
\affil[1]{\normalsize University of Oxford} %\href{mailto:francis.ditraglia@economics.ox.ac.uk}{francis.ditraglia@economics.ox.ac.uk}}
\affil[2]{\normalsize University of California San Diego}
%\href{mailto:ctmcintosh@ucsd.edu}{ctmcintosh@ucsd.edu}}
\affil[3]{\normalsize Harvard University}
%\href{mailto:isaacmezalopez@g.harvard.edu}{isaacmezalopez@g.harvard.edu}}
\affil[4]{\normalsize ITAM}
%, \href{mailto:jsadka@itam.mx}{jsadka@itam.mx}}
\affil[5]{\normalsize University of Notre Dame}

\date{\today \\[2 cm]}

@@

\begin{abstract}
%We explore the merits of structured repayment contracts in the understudied context of pawn lending. We use a novel one-stage, three-armed RCT, including mandatory and voluntary treatment arms, to point-identify the effects of regular monthly payments both for individuals who would freely choose, and would not freely choose, structured payments. We find that assigning borrowers to commitment-style contracts decreases the financial cost of pawn loans by 22\% and increases the likelihood of recovering their pawn by 15\%. However, only 11\% of borrowers choose such contracts voluntarily. We find that borrowers who would \textit{not} choose regular payments would benefit substantially from getting such contracts, as much as those freely choosing them (no selection on gains).  A paternalistic policy mandating structured payments helps a sufficiently large fraction of borrowers that it cannot be improved upon by feasible personalized targeting. 
\singlespacing
Pawn loans offer borrowers a high degree of repayment flexibility in exchange for a harsh penalty in case of default: forfeit of collateral worth more than the loan amount. Using a large RCT conducted in Mexico City, we document key stylized facts and explore the merits of replacing flexibility with structured repayment contracts in this important but understudied form of credit. 
A novel experimental design that includes a mandatory frequent-payments arm, a (status quo) flexible payments arm, and a choice between the two, point-identifies not only the average treatment effect, but also the effects of treatment on the treated and the untreated along with the average selection on gains, allowing a rigorous study of mandates versus choice. Although the average treatment effect of assigning borrowers to structured payments is a 22\% decrease in their financial cost and a 15\% increase the probability that they will recover their pawn, only 11\% of borrowers choose structured repayment contracts voluntarily. We show that structured repayment benefits nearly all borrowers, including those who would not freely choose it, and find no evidence of selection on gains. 
%Nonetheless, lenders' profits are lower under structured payments since they earn more from borrower default, giving lenders little incentive to offer such contracts.

\end{abstract}

%\vspace{.6in}
\noindent \textbf{Keywords: } Mandates versus choice, paternalism, treatment on the untreated, payment frequency, overconfidence.\\ \textbf{JEL codes:} G41, C93, O16, G21

@@

\forES{Enrique please do this}

\forIM{Please that}

Pawn lending is one of the oldest and most prevalent forms of credit in the world \citep{carter2012pawnshops}. Pawn loans are typically small, and short-term. They involve no credit checks or proof of income, and are widely used by people without access to other forms of credit. Borrowers surrender highly liquid collateral as the pawn, typically gold, in return for a loan that is substantially smaller than their pawn's value.  These loans are very flexible: there are no scheduled payments, no prepayment penalties, and interest is charged only on outstanding balance. Unlike mortgage lenders, pawn lenders retain the entire value of the collateral under default along with any payments already made, rather than simply recovering the outstanding value of the loan.  There are more than 11,000 pawn shops across the US with 30 million clients and \$14 billion yearly revenues; in China pawn lending is a 43 billion dollar industry.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}. In Mexico the scale of pawn lending rivals that of microfinance: during the past three years a single large lender in the country made over 4 million loans to more than a million clients, compared to a total of 2.3 million microfinance clients in all of Mexico during 2009 \citep{Pedroza:2010}.}  Despite this, pawnshops have received little attention in the literature to date.

Pawn loans are different from conventional credit in important ways. First, pawn loans typically default at much higher rates than other forms of credit. For example, 44\% of loans made by our partner lender are not repaid, and 29\% of those who fail to repay make payments prior to defaulting, money which is completely lost to them subsequently. Second, lender profits are higher under default than repayment. An industry standard contract in Mexico City lends 70\% of the value of gold collateral at an interest rate of 7\% for three months. Because gold is highly liquid, the profit from a borrower who defaults is 30\% of the collateral value compared to 22.5\% in interest if a loan is paid in full on the last day.   Furthermore, pawn borrowers are typically economically vulnerable and, in our context, are also naively optimistic; borrowers report a subjective probability of repayment that averages 92\%. The unusual degree of flexibility in these contracts would benefit borrowers if they were neo-classical agents, but the prevalence of costly default that hurts borrowers but benefits lenders, combined with apparently naive borrowers, calls this into question. Other lending modalities with dramatically lower equilibrium default, such as microfinance, typically rely on highly structured repayment regimes.
%Hence pawn lending features unusual dynamics, and lender incentives are quite different from other forms of lending.

%Much of the literature on standard credit contracts has illustrated that structured repayment schedules help borrowers avoid default \citep{morduch1999microfinance}.  Indeed, \cite{Laibson2018} has discussed the many ways in which forcing devices like structure and deadlines are embedded into schools, workplaces, and financial institutions so as to improve outcomes whether or not the customers would have freely elected these features.  Pawn lending, in contrast with the highly structured contracts of microfinance lending, typically features no reminders or regular payment schedule, with borrowers required to remember to make a single balloon payment withing the contracted time or else lose the pawn.  Given this combination of issues, it appears possible that the lack of structure in pawnshop lending is strategic on the part of lenders.  This raises the possibility of potential gains to borrowers by introducing contracts with more regularized repayment structure.

%Financial institutions often use built-in commitment mechanisms like fixed repayment streams to lower default rates and increase their own profits. At the same time, they frequently ``shroud'' these attributes by embedding them as non-negotiable features of the loan contract, presumably because borrowers undervalue commitment and would not demand it, given the choice. \cite{Laibson2018} refers to this practice as ``private paternalism''. When the incentives of firm and client align, as they do in \cite{Laibson2018}, private paternalism can benefit both parties. Pawn lending, however, turns this idea on its head: since the value of the collateral--the pawn--exceeds that of the loan, lenders stand to gain the most when borrowers default.Consistent with this idea, and in stark contrast to microfinance, pawn lenders in Mexico City neither send payment reminders to borrowers nor provide commitment features in their contracts. Default is common.\footnote{The default rate in the \emph{status quo} arm of our Mexico City experiment is 44\%.}

This paper asks whether structured repayments can help pawnshop borrowers avoid default.  To do so, we present a unique three-armed experiment covering around 4,500 pawnshop clients across six of our partner lender's Mexico City branches.  Borrowers in the Control arm received the standard status quo pawn contract (described above) which allows us to document payment trajectories and default in standard pawn markets.  Borrowers in the `Structured' arm were required to make three monthly payments, with each monthly payment including the accrued interest at that time, and faced a nominal fee of 2\% of that month's payment if the payment was delinquent.  Borrowers in the `Choice' arm were allowed to choose between the Standard and Structured contracts.   A design that features both assignment and choice permits a nuanced understanding of how treatment effects relate to the choices that individuals freely make: because our context featured no differential selection of clients across arms, we can recover a unique combination of economically-relevant causal estimands.\footnote{See Section \ref{sec:integrity} for details.}

Comparing the Structured and Control arms gives the Average Treatment Effect (ATE) of structured repayment in the pawnshop context.  Comparing the Choice arm to the Control provides a standard Intention to Treat (ITT) effect of offering this option.  The presence of all three arms in the same experiment then allows us to point identify treatment effects \emph{separately} for those who would and would not choose structure, given the choice.  Consider only the Control and Choice arms. No one in the Control arm is treated, but some borrowers in the Choice arm choose to be treated: choosers. We can view the comparison of these two arms as an experiment with one-sided non-compliance. Here assignment to the choice arm serves as an instrumental variable for treatment receipt. Under an exclusion restriction, a familiar argument shows that the IV estimator identifies the causal effect for people who are shifted by the instrument: choosers. This is the Treatment on the Treated (TOT).  Now consider only the Choice and Structured arms. Everyone in the Structured arm is treated, but some borrowers in the Choice arm choose not to be treated: non-choosers. We can view the comparison of these two arms as a separate experiment, also with one-sided non-compliance. Here assignment to the Structured arm serves as an instrumental variable for treatment receipt. Under a symmetric exclusion restriction, an almost identical argument shows that the IV estimator identifies the causal effect for people who are shifted by the instrument: non-choosers. This is the Treatment on the Untreated (TUT).  As far as we are aware, this is the only experimental paper that provides a direct comparison of the TUT and TOT in the same context.  This comparison is key for studying voluntary versus mandatory treatment.

%\todo[inline]{Should add a bit more on the ``mandates versus choice'' design here, including some other possible scenarios where it could be employed: education experiment, 401k, online privacy settings.}

This design reveals critical information about marginal treatment effects and selection on gains, and is useful for any circumstance in which we want to compare voluntary versus mandated compliance.  In educational settings, it may be useful to understand whether providing optional exercises in advance of a major exam is sufficient, or whether it is more effective to require students to complete these.  In the much-studied context of employer-based retirement savings plans, this design can be used to examine the relative benefits of providing options for higher and earlier employee contributions versus simply defaulting employees into more aggressive savings plans.  Digital service providers trying to understand how digital privacy settings drive platform engagement and monetization could either provide choices to consumers or simply default them into stricter protections, and our design provides a way of comparing the relative benefits of these approaches.  In general, our method for testing the TOT against the TUT provides a practical way of understanding how treatment effect heterogeneity relates to real-world compliance decisions.

%while comparing.  Invoking the standard exclusion restriction, we can calculate the Treatment on the Treated (TOT) for choosers in the Choice arm.  Novel to this context is that we can then use a symmetric assumption to calculate the Treatment on the Untreated (TUT) by comparing the Choice and Assigned arms to each other.  Thus, in a single context and with minimal assumptions, this design allows us to compare the treatment effects for individuals who would have and would not have freely chosen the treatment.  %We provide Stata code to conduct correct inference on the comparison of the TOT and the TUT, which is the relevant comparison for any applied policy conversation about the relative benefit of offering a policy versus imposing it upon agents.
%\textcolor{teal}{We explain in the paper why the estimation of TUT is essential to assess the pros and cons of mandating a contractual feature (in our lexicon, imposing a mandate and eliminating choice is a form of paternalism).}

%ompared to the status quo arm that continues to receive the standard pawn contract, we that answers three key questions. First, does the absence of commitment-style contracts cause default in pawn lending? If so, to what extent does this benefit lenders? Second, if a commitment contract were available would pawn borrowers choose it? Even more importantly, would the \emph{right} borrowers choose it, i.e.\ those who would benefit the most? Third, is there a case for \emph{paternalism}, namely for mandating commitment in pawn lending? If so, should commitment be mandated for all borrowers or can it be effectively targeted? The question of choice versus paternalism is particularly salient in a setting with vulnerable borrowers. Yet comparing voluntary versus paternalistic policies is challenging. Even if commitment lowers financial costs on average, it may be ineffective or even harmful for borrowers who \emph{would not choose} to commit. To meet this challenge we introduce a novel three-armed design, the ``forcing-choice'' design, that allows us to shed light on these three questions in the important and under-studied context of pawn lending.

%Our experiment covers just under 5,000 pawnshop clients across six of our partner lender's Mexico City branches. The control arm illustrates the costs of the \emph{status quo} contract: fully 44\% of control borrowers default, losing their pawn along with any payments made towards principal. Worse still, 29\% of those who default do so after making at least one payment towards recovery, a payment that they forfeit upon default. The ``forced commitment'' arm requires borrowers to make three monthly payments, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent.  Finally, the ``commitment choice'' arm offers borrowers the chance to opt in to the same structured monthly contract that is mandated for borrowers in the forced commitment arm.\footnote{When describing this new contract below, we use the terms ``commitment'' and ``structured payment'' interchangeably.}

%Because there is no selection into or out of the control (status quo) and forced commitment arms in our experiment, the forcing-choice design can be viewed as a \emph{juxtaposition} of three more familiar experimental designs.\footnote{See section \ref{sec:integrity} for a discussion of how we can be sure that there was no selection into or out of the treatment and forced commitment arms.} The first is a standard two-armed RCT with perfect compliance that point identifies the average treatment effect (ATE) of commitment. The other two are a pair of randomized encouragement designs, each with one-sided non-compliance: one point identifies the effect of commitment for borrowers who would \emph{voluntarily} choose commitment (treatment on the treated: TOT), while the other point identifies the effect of commitment for borrowers who would \emph{not} (treatment on the untreated: TUT). Fully evaluating the case for paternalism versus borrower choice requires policymakers to learn not only whether those who demand commitment benefit from it (TOT), but also whether those who \emph{do not} are better off without it (TUT).

Our ATE results show that mandatory structured payments are strongly effective in lowering financial costs to borrowers and preventing default in pawnshop lending: the average borrower in the Structured arm pays financing costs inclusive of fees that are 22\% lower than the control, and faces a probability of default that is 6.6 percentage points lower (15\% of the mean). In terms of Annual Percentage Rates (APR), the financial cost of borrowing falls by 11 percentage points per loan (19\% of the mean). In short, structured repayment saves borrowers money by charging them fees. The mechanism by which our monthly payment contract achieves these cost savings is intriguing: not only does it improve repayment and speed up the pace of payments on average, but it also decreases the amount of money paid by borrowers who will ultimately go on to default. While we find that borrowers who experience structured payment contracts are 6 percentage points more likely to borrow again from the same lender, a back-of-the-envelope calculation suggests that the structured contract nevertheless lowers lender profits by at least 14\% per borrower. It is thus unsurprising that structured payment contracts were unavailable in Mexico city pawnshops outside of our experiment: lenders profit from default.\footnote{Unlike most pawn lenders, our partner operates as a non-profit, donating all of their earnings to philanthropic causes.}

%Given the limited measures that are available to us, we refrain from making definitive welfare statements in this paper, focusing instead on the cost of loan servicing, an important outcome in credit markets.\footnote{\hl{Enrique will find citations for a defensive footnote that goes here, pointing out that lots of papers use this as an outcome measure.}} Nevertheless, we explore the sensitivity of our findings to broader notions of cost. For example, our results are qualitatively robust to deducting transport costs of visiting the branch to make interim payments along with a day of lost wages for each visit. They are also robust to using borrowers' \emph{subjective} values of their pawns rather than the appraised value and to adjusting for lost liquidity from requiring monthly payments.

Despite the large financial cost savings that it provides, there is low demand for structured repayment: only 11\% of borrowers in the choice arm choose structure. The mystery is then why so few people choose a contract that is financially beneficial on average.  Could it be that this small fraction of ``choosers'' simply represents the only individuals who benefit from structure?  The strongly significant difference between the Structured arm and the Choice arm suggests that this is not the case.  More rigorously, an exercise that non-parametrically bounds the distribution of individual treatment effects, following \cite{fan2010sharp}, shows that structured repayment benefits more than twice the number of people who chose it, even under the most conservative assumptions. Imposing the two exclusion restrictions \hl{mentioned above} \forFdT{We did not mention them above} allows us to go further, point identifying the average treatment effects for choosers (TOT) and non-choosers (TUT) along with the average selection on gains ($\text{ASG} = \text{TOT} - \text{TUT}$), a measure of the empirical relevance of Roy-type selection.  Our estimated TOT implies that choosers actually see a very small and insignificant increase in the cost of their loans from structure. \forCM{FC is not that small} The TUT effect, in contrast, suggests that the financial cost savings to non-choosers are large: \$192 pesos, equivalent to a 10.6 percentage point savings in APR. On average, the borrowers who would \emph{not} choose commitment, would have faced substantially lower financial costs if they had. We find no evidence of selection on gains. Finally, we combine our experimental treatment and outcome data with survey responses collected for a subset of borrowers to estimate conditional average treatment effects, both TUTs and ATEs, using the Causal Random Forest algorithm of \cite{atheygrf}. We estimate positive conditional average TUT effects for 93\% of the borrowers who did \textit{not} choose the structured contract. In short, it is extremely difficult to find identifiable groups of borrowers who incur higher financial costs under a structured contract, even when restricting attention to those who would not choose it voluntarily
